Example gene set analysis

### 2021-09-03 example.Rmd
Figure 1 edits

plot(euler(v0),quantities = TRUE,main="effect of combining up and down regulated genes")

@@

plot(euler(v1),quantities = TRUE, main="FCS compared to ORA")

@@

plot(euler(v2),quantities = TRUE, main="Effect of inappropriate background* (whole genome)")

@@

plot(euler(vx),quantities = TRUE, main="combining up and down genes and whole genome bg*")

@@

plot(euler(v3),quantities = TRUE, main="all sets")

png("images/fcs_ora1.png")
plot(euler(v1),quantities = TRUE, main="FCS vs ORA")
dev.off()

png("images/orabg1.png")
plot(euler(v2),quantities = TRUE, main="Effect of inappropriate background* (whole genome)")
dev.off()

@@

>>>>

plot(euler(v0),quantities = TRUE, edges = "gray", main="effect of combining up and down regulated genes")

@@

plot(euler(v1),quantities = TRUE, edges = "gray", main="FCS compared to ORA")

@@

plot(euler(v2),quantities = TRUE, edges = "gray", main="Effect of inappropriate background* (whole genome)")

@@

plot(euler(vx),quantities = TRUE, edges = "gray", main="combining up and down genes and whole genome bg*")

@@

plot(euler(v3),quantities = TRUE, edges = "gray", main="all sets")

png("images/fcs_ora1.png")
plot(euler(v1),quantities = TRUE, edges = "gray", main="FCS vs ORA")
dev.off()

png("images/orabg1.png")
plot(euler(v2),quantities = TRUE, edges = "gray", main="Effect of inappropriate background* (whole genome)")
dev.off()

@@

pdf("images/fcs_ora1.pdf",width=4,height=4)
plot(euler(v1),quantities = TRUE, edges = "gray", main="FCS vs ORA")
dev.off()

pdf("images/orabg1.pdf",width=4,height=4)
plot(euler(v2),quantities = TRUE, edges = "gray", main="Effect of inappropriate background* (whole genome)")
dev.off()

pdf("images/oracomb1.pdf",width=4,height=4)
plot(euler(vx),quantities = TRUE, edges = "gray", main="combining up and down genes and whole genome bg*")
dev.off()
